Supplement to Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-02-19 supplement.tex
I added a more careful analysis of the airmass trend analysis near telluric feature.

>>>>

\clearpage
\section{Airmass Correlation}
One thing to check is that the U shaped light curves near the telluric water bands are correlated to airmass.
As I start, I took a time series at 1.26~$\mu$m to remove find a trend-line for brown dwarf modulations.
This is shown in Figure \ref{fig:1p26umFluxTrendFit}.
I then remove this polynomial trend from the 1.38~$\mu$m time series to remove the brown dwarf oscillations from it.
The residual light curve has a U shape similar to the airmass trend shown in Figure \ref{fig:1p38residAndAirmass}.
A direct correlation plot is shown in Figure \ref{fig:residAirmass1p38corr}.

\begin{figure*}[!t]
\centering
\subfloat[Flux at 1.26~$\mu$m for the Trend-line]{
	\includegraphics[width=0.5\textwidth]{images/airmass/trendline_1p26um.pdf}
	\label{fig:1p26umFluxTrendFit}
	}
\subfloat[Flux at 1.38~$\mu$m and Airmass]{
	\includegraphics[width=0.5\textwidth]{images/airmass/airmass_1p38um_resid_simult.pdf}
	\label{fig:1p38residAndAirmass}
	}
	\caption{In order to investigate correlations with airmass at 1.38~$\mu$m, I first fit the 1.26~$\mu$m time series with a 10th order polynomial fit.
	I then use the polynomial fit to remove most of the brown dwarf related oscillations in the time series at 1.38$\mu$m. The residuals show a U shape similar to the airmass table.}
	\label{fig:airmassTimeSer1p38}
\end{figure*}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/airmass/airmass_flux_correlation.pdf}
\caption{Time series at 1.38$\mu$m as a function of airmass, where the brown dwarf oscillations are mostly removed as described in Figure \ref{fig:airmassTimeSer1p38}.}\label{fig:residAirmass1p38corr}
\end{centering}
\end{figure}
